Bird beak's elaboration and exploration

### 2022-02-24 Analysis/02-MCMCglmm_mini_chains.Rmd
Update 02-MCMCglmm_mini_chains.Rmd

```{r install_beer, eval = FALSE}
## Installing beer
devtools::install_github("TGuillerme/elaboration_exploration_bird_beaks/beer")
```

@@

<!--

#### Number of runs optimisation (TO BE DEVELOPED?)

```{r, eval = FALSE}
## Function for running one mini chain on a random tree (and saving the results)
fun.mini.chains <- function() {
    run.mini.chains(mini_chains, replicates = 1, path = "../Data/Processed/MCMC/", file.name = "mini.chains")
}
```

To make sure we reached consistent results, we run the set of N mini-chains were N was determined using the following variance optimisation algorithm.

 * 1. run an initial $N = 20$ chains;
 * 2. estimate the $V_{1}$, the pooled variances for each parameters in the chain (V1 is a vector of length §§§);
 * 3. update N to N = N * 1.05 and run an additional 5% chains;
 * 4. estimate $V_{2}$, the pooled variances for each parameters in the chain;
 * 5. calculate $\Delta_V$, the absolute change between $V_{1}$ and $V_{2}$ as ($\sqrt{(\frac{V_{1}}/{V_{2}} - 1)^{2}}$).
 * 6. If $\Delta_V < 0.05$ (meaning an increase of 5% of the replicates resulted in an increase of the parameters of less than 5%), the desired number of mini-chains is reached. Else, set $V_{1} = V_{2}$ and repeat from step 3.

```{r, optimised_replicates, eval = FALSE}
## The summary function

```

After reaching the desired $N$ chains, we pulled all the posterior estimates together back into a "standard" big MCMCglmm with a posterior distribution including the effective results and the phylogenetic uncertainty.

-->

>>>>

```{r install_beer, eval = FALSE}
## Installing beer
devtools::install_github("TGuillerme/elaboration_exploration_bird_beaks/mcmcmcglmmm")
```

@@
